Practice proofs \#5

### 2018-10-02 practice-proofs/PracticeProofs5.tex
Correction to practice proofs 5.

\subsection*{Cardinality and subsets}

@@

\subsection*{Countable unions of sets}

We study the cardinality of ordinary and disjoint unions of countable sets.

\begin{lem} \label{lem:CountableUnions1}
	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
\end{lem}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Direct proof.
	%------------------------------------------%
\end{proof}

\begin{prop} \label{prop:CountableUnions2}
	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigsqcup_{j\in J} A_j = \aleph_0.
	$$
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Start by recalling the definition of disjoint union. Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
	%------------------------------------------%
\end{proof}

\begin{prop} \label{prop:CountableUnions3}
	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigcup_{j\in J} A_j \leq \aleph_0.
	$$
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Direct construction.
	%------------------------------------------%
\end{proof}

\subsection*{Cardinality and power sets}

We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$. Think about the process of taking the image of $S$ in $f$. Is that a function of $S$?
	%------------------------------------------%
\end{proof}

>>>>

We study how cardinality interacts with subsets and power sets.

Recall that we say that two sets are equinumerous if they have the same cardinality.
The following proposition says that the operation ``take the power set'' preserves equinumerosity.

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: There must be a bijection $f:X\to Y$.
	% Pick an arbitrary $S\subset X$.
	% Think about the process of taking the image of $S$ in $f$.
	% Is that a function of $S$?
	%------------------------------------------%
\end{proof}

@@

\begin{cor} \label{cor:IntersectionCardinality}
	$\# (X\cap Y) \leq \# X$.
\end{cor}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Use proposition~\ref{prop:SubsetCardinality}.
	%------------------------------------------%
\end{proof}
